Model

### 2020-03-06 stats/model.Rmd
add experiments to supplementary file

```{r}
library(tidyverse)
library(rwebppl)
#library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
#library(langcog)

@@

x_fb <- sample(1:length(unique(model_pred_prag_fb$iteration)), 100)

plot_model_prag_line_fb <- model_pred_prag_fb%>%
  filter(iteration %in% x_fb)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)),size = .2, alpha = .1)+
  geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)

@@

@@

com_item_params <- bind_rows(
  item_params%>%mutate(model="pragmatic"),
  item_params_fb%>%mutate(model="fullBayes")
)

ggplot(com_item_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")

@@

@@

>>>>

```{r}
library(tidyverse)
library(rwebppl)
#library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

@@

x_fb <- sample(1:20000, 50)

plot_model_prag_line_fb <- readRDS("../saves/model_pred_prag_fb.rds")%>%
  filter(iteration %in% x_fb)%>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

ggplot() +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(data = data_comb, aes(x = age_num, y = correct), alpha = .1, height = .025, width = 0)+
  geom_line(data = plot_model_prag_line_fb, aes(x=age+2,y = pred, col = alignment, group = interaction(alignment,chain,iteration)),size = .2, alpha = .2)+
  geom_pointrange(data = binned_data, aes(x = subage+0.5, y = data_mean, ymin = data_ci_lower, ymax = data_ci_upper), pch = 5)+
    geom_line(data = binned_data, aes(x = subage+0.5, y = data_mean))+
 # geom_smooth(data = data_comb_plot, aes(x = age_num, y = correct, col = alignment, lty = alignment), method = "glm", method.args = list(family = "binomial"), se = F, alpha = .5, span = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.09,1.09)+
  xlim(2,5)+
  guides(alpha = F, fill = F)+ 
  scale_colour_ptol()+
  theme(legend.position = "bottom")

@@

```{r}
binned_data <- data_comb%>%
  group_by(subage, alignment, item)%>%
  summarize(k = sum(correct), n = n())%>%
  ungroup() %>%
  mutate(a = 1 + k,
         b = 1 + n - k,
         data_mean = (a-1)/(a+b-2),
         data_ci_lower  = qbeta(.025, a, b),
         data_ci_upper = qbeta(.975, a, b),
         age = factor(subage))%>%
  select(-a,-b,-n,-k)

@@

com_item_params <- bind_rows(
  item_params%>%mutate(model="pragmatic"),
  item_params_fb%>%mutate(model="fullBayes"),
  item_params_mm%>%mutate(model="mixture"),
  item_params_dmm%>%mutate(model="mixture_dev")
)

ggplot(com_item_params, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter ~ item, scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")+
  scale_fill_ptol()

@@

```{r}
ggsave("../graphs/comparison_item_params.pdf", width = 12, height = 8, scale = 1.5)
```

@@

com_global_sigmas <- bind_rows(
  item_sigma%>%mutate(model="pragmatic"),
  item_sigma_fb%>%mutate(model="fullBayes"),
  item_sigma_mm%>%mutate(model="mixture"),
  item_sigma_dmm%>%mutate(model="mixture_dev")
)

ggplot(com_global_sigmas, aes(x = value, fill = model, group = paste(model,chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(type ~ ., scales = 'free')+
  theme_few()+
  theme(legend.position = "bottom")+
  scale_fill_ptol()
```
